Sound and Automated Synthesis of Digital Controllers for Physical Plants

### 2016-10-08 paper/paper.tex
add controller c_4 for the experimental evaluation
improve Description of Benchmarks
cite in ascending order

In order to synthesise closed-loop digital control systems, we use a
program synthesis engine.  Nowadays, such engines are used
increasingly often in program verification
\cite{DBLP:conf/cav/0001A14,DBLP:conf/lpar/DavidKL15}.  Our program
synthesiser makes use of Counter-Example Guided Inductive Synthesis
(CEGIS) \cite{sketch}.  We start by presenting its general
architecture followed by describing the parts specific to control
systems.

@@

>>>>

In order to synthesise closed-loop digital control systems, we use a
program synthesis engine.  Nowadays, such engines are used
increasingly often in program verification
\cite{DBLP:conf/lpar/DavidKL15,DBLP:conf/cav/0001A14}.  Our program
synthesiser makes use of Counter-Example Guided Inductive Synthesis
(CEGIS) \cite{sketch}.  We start by presenting its general
architecture followed by describing the parts specific to closed-loop control
systems.

@@

The discrete controllers $C_{4}$ and $C_{5}$ for the satellite plant $G_{3}$ 
are represented by the following z-expression:
%
\begin{equation}
\label{satellite-b2}
C_{4}(z)=\frac{2.88z^2 - 4.896z + 2.074}{1.0z^2 - 0.42z - 0.3465 - 0.03915}. \nonumber
\end{equation} 
%
\begin{equation}
\label{satellite-c2}
C_{5}(z)=\frac{0.43z^2 - 0.2408z - 0.1316}{1.0z^2 + 1.5z + 0.97 + 0.183}. \nonumber
\end{equation}
